Kyoto VR MQP Paper First Draft

### 2019-09-24 paper.tex
add API documentation appendix

\usepackage{lipsum}   % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
%\usepackage{minted}
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
\usepackage[page, titletoc, title]{appendix}
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref}      % hyperlinks

@@

@@

@@

The user can easily create a new region by shift-clicking, and then clicking
points on the map.  To terminate the polygon, the user must shift-click again.
The ``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
these instructions, which should be enough to get started.  A user can only
terminate the polygon after two points have been placed to prevent the user
from drawing a region with an area of zero. Once a region is created, a region
card appears in the side bar. From here, the user can edit anything about the
region. From here, the user can edit anything about the region.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{welcome-card-editour.png}
    \caption{The ``Welcome to Editour'' card providing basic instructions to
    get started}
	\label{fig:welcomeCard}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
    \caption{How the Editour looks when a region is being drawn, including the
    two dotted preview lines}
	\label{fig:drawingRegion}
\end{figure}

@@

The first subcard seen in Figure~\ref{fig:renameSubcard} is the ``Rename''
subcard, which is fairly self-explanatory.  This section expands to reveal a
textbox, allowing the user to rename the region after clicking ``Okay'' or
hitting the enter key. (There are multiple places in the UI where a textbox is
immediately adjacent to a ``Confirm'' button.  We made sure all of these can be
triggered by simply hitting enter, since this is common when filling out
forms.)

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{rename-subcard-editour.png}
	\caption{The ``Rename'' subcard}
	\label{fig:renameSubcard}
\end{figure}

The second subcard seen in Figure~\ref{fig:mediaSubcard} is slightly involved.
Expanding the ``Media'' subcard by clicking on the green bar will reveal a bevy
of options for augmenting the audio, images and text to be associated with that
region of the tour. From here, the user can upload an audio file and multiple
image files from his or her hard drive with the two file-select fields. If the
tour has been downloaded as a server, the names of the files already present on
the server will appear as cards with `X' buttons. This allows the user to
remove images or audio from that region even after the tour has been uploaded.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{media-subcard-editour.png}
	\caption{The ``Media'' subcard}
	\label{fig:mediaSubcard}
\end{figure}

@@

\begin{figure}[h]
	\centering
    \includegraphics[width=\textwidth]{edit-subcard-with-map-editour.png}
    \caption{The ``Edit'' subcard with the map showing vertices and edges that
    can be edited}
	\label{fig:editSubcardWithMap}
\end{figure}

The third subcard pictured in Figure~\ref{fig:deleteSubcard} is the ``Delete''
subcard. When revealed, another button will appear labeled ``Really Delete''.
The action can be canceled by collapsing the subcard by hitting the bar now
labeled ``Don't Delete!''. This prevents the user from accidentally deleting a
region he or she did not mean to.

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{delete-subcard-editour.png}
    \caption{The ``Delete'' subcard}
	\label{fig:deleteSubcard}
\end{figure}

Above all of the region cards, there are various options for uploading,
downloading, renaming and deleting tour files on the server. Within the upload,
download and delete cards there are message boxes to indicate the status of
that operation. When uploading and downloading, a percentage will be displayed
indicating the upload/download process, which can be seen in
Figure~\ref{fig:uploadingMessage}. If a 200 or 201 is returned from the server,
a ``Success'' message will appear. If there was some problem, the error message
returned by the server is displayed in this box instead. Since uploading,
downloading and deleting are all network-related operations, it makes sense to
include this message box for each card.

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{uploading-message-editour.png}
    \caption{The upload subcard with an upload status}
	\label{fig:uploadingMessage}
\end{figure}

When the page is loaded, the frontend will request the names of the files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking
on one of these blue buttons will fill the textbox in with the correct name.
Before this feature was implemented, the user had to correctly type the name of
the saved tour into the textbox in order to retrieve it. The user is still free
to do this, but the buttons make this easier and less error-prone. The download
card containing a box filled with filenames on the server can be seen in
Figure~\ref{fig:downloadCard}.

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{download-card-editour.png}
    \caption{The download card}
	\label{fig:downloadCard}
\end{figure}

We did not include a way to resolve addresses or place names, like the service
provided by Google Maps. Instead of exploring plugins/libraries that might
provide this functionality, we offered a simpler solution due to time
constraints.  You can type in a latitude and longitude directly and hit the
``Jump'' button. We also hard-coded a few shortcuts for places that Atticus
might want to design a tour for in the future, which can be accessed by
clicking on the yellow buttons with place names.

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{jump-card-editour.png}
    \caption{The jump card}
	\label{fig:jumpCard}
\end{figure}

@@

As previously mentioned in \ref{sec:editingATour}, our web application allows
users to edit existing tours. When the user requests to edit a tour on the
frontend it sends a request to the backend server for that tour's metadata
file. This file contains information about all regions and files in the tour.
The user can then edit the regions, change names, upload new files, or delete
existing ones without ever having to download the other tour files from the
server, which could take a long time depending on their size. When the user is
done editing they can upload the new metadata and any newly added files to the
server, which intelligently collects new and old files required by the tour and
zips them into a new tour file on the disk.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\textwidth]{intersections-diagram.png}
	\caption{A visualization of the algorithm}
	\label{fig:intersectionsDiagram}
\end{figure}

@@

% \begin{figure}[h]
%	\centering
%	\includegraphics[width=\textwidth]{turtle-burger.jpg}
%	\caption[A rare but delicious turtle burger in the wild]{A rare but
%		delicious turtle burger in the wild~\autocite{harvey2002}.}
%	\label{fig:turtleBurger}
%\end{figure}

@@

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

\section{}
Appendix two text goes here.

>>>>

\usepackage{lipsum}   % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
\usepackage[page, titletoc, title]{appendix}
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref}      % hyperlinks

@@

% custom environment for indenting whole paragraphs
\newenvironment{indented}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

@@

\subsubsection{KudanSlam}
\label{sec:kudanSlam}

@@

The user can easily create a new region by shift-clicking, and then clicking
points on the map.  To terminate the polygon, the user must shift-click again.
The ``Welcome to editour'' card provides these instructions, which should be
enough to get started.  A user can only terminate the polygon after two points
have been placed to prevent the user from drawing a region with an area of
zero. Once a region is created, a region card appears in the side bar. From
here, the user can edit anything about the region. From here, the user can edit
anything about the region.

@@

The first subcard is the ``Rename'' subcard, which is fairly self-explanatory.
This section expands to reveal a textbox, allowing the user to rename the
region after clicking ``Okay'' or hitting the enter key. (There are multiple
places in the UI where a textbox is immediately adjacent to a ``Confirm''
button.  We made sure all of these can be triggered by simply hitting enter,
since this is common when filling out forms.)

The second subcard is slightly involved. Expanding the ``Media'' subcard by
clicking on the green bar will reveal a bevy of options for augmenting the
audio, images and text to be associated with that region of the tour. From
here, the user can upload an audio file and multiple image files from his or
her hard drive with the two file-select fields. If the tour has been downloaded
as a server, the names of the files already present on the server will appear
as cards with `X' buttons. This allows the user to remove images or audio from
that region even after the tour has been uploaded.

@@

The third subcard is the ``Delete'' subcard. When revelead, another button will
appear labeled ``Really Delete''. The action can be canceled by collapsing the
subcard by hitting the bar now labeled ``Don't Delete!''. This prevents the user
from accidentally deleting a region he or she did not mean to.

Above all of the region cards, there are various options for uploading,
downloading, renaming and deleting tour files on the server. Within the upload,
download and delete cards there are message boxes to indicate the status of
that operation. When uploading and downloading, a percentage will be displayed
indicating the upload/download process. If a 200 or 201 is returned from the
server, a ``Success'' message will appear. If there was some problem, the error
message returned by the server is displayed in this box instead. Since
uploading, downloading and deleting are all network-related operations, it
makes sense to include this message box for each card.

When the page is loaded, the frontend will request the names of the files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking on
one of these blue buttons will fill the textbox in with the correct name. Before
this feature was implemented, the user had to correctly type the name of the
saved tour into the textbox in order to retrieve it. The user is still free to
do this, but the buttons make this easier and less error-prone.

We did not include a way to resolve addresses or place names, like the service
provided by Google Maps. Instead of exploring plugins/libraries that might
provide this functionality, we offered a simpler solution due to time
constraints.  You can type in a latitude and longitude directly and hit the
``Jump'' button. We also hard-coded some shortcuts for places that Atticus
might want to design a tour for in the future, which can be accessed by
clicking on the yellow buttons with place names.

@@

Additionally, our web application allows users to edit existing tours. When the
user requests to edit a tour on the frontend it sends a request to the backend
server for that tour's metadata file. This file contains information about all
regions and files in the tour. The user can then edit the regions, change names,
upload new files, or delete existing ones without ever having to download the
other tour files from the server, which could take a long time depending on
their size. When the user is done editing they can upload the new metadata and
any newly added files to the server, which intelligently collects new and old
files required by the tour and zips them into a new tour file on the disk.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{intersections-diagram.png}
	\caption{A visualization of the algorithm}
	\label{fig:intersectionsDiagram}
\end{figure}

@@

@@

\appendices
\section{Editour API Documentation}

Here is a list of API functions the Editour backend handles. The response is
usually a JSON like this with fields called \texttt{status} and \texttt{message}
The status is an HTTP status code like 200 (OK) or 404 (Not Found), and the
message is a string or stringified JSON that contains the data of the response.

\noindent\textbf{GET \texttt{/edit/:name}}

\begin{indented}{1cm}
	Returns the metadata file of the most recent tour with the given name. If
	successful, it returns a status of 200 and the stringified metadata as the
	message. If no tour with the given name is found it returns 404, and if the
	server encounters an internal error while processing the request it returns
	500.
\end{indented}

\noindent\textbf{GET \texttt{/tour/:name}}

\begin{indented}{1cm}
	This is the only API endpoint for which the response is not a JSON. Instead,
	the response is the zip file of the most recent version of the tour with the
	given name. Returns 404 if a tour with the given name isn't found or a 500
	if there is an internal server error while processing the request.
\end{indented}

\noindent\textbf{GET \texttt{/tours}}

\begin{indented}{1cm}
	Gets a list of unique tours on the server, returning a list of their names
	as the message of its response. Returns 200 if successful or 500 if there is
	an internal server error while processing the request.
\end{indented}

\noindent\textbf{POST \texttt{/edit}}

\begin{indented}{1cm}
	Used for editing an existing tour. This request should contain the fields
	\texttt{tourName}, \texttt{oldName}, and \texttt{metadata}, along with any
	number of files.  The server will use the new metadata as well as the old
	and new files to create a new version of an existing tour. Returns 201 if
	the tour was edited successfully, 400 if the request was invalid, 404 if the
	requested tour couldn't be found, or 500 if a server error occurred while
	processing the request.
\end{indented}

\noindent\textbf{POST \texttt{/upload}}

\begin{indented}{1cm}
	Used for uploading a new tour. This request should include a
	\texttt{tourName} field and a \texttt{metadata} field, along with any number
	of files. It verifies the uploaded tour and creates a zip for it on the
	server. Sends a 201 if the tour was created successfully, a 400 if the
	request is invalid, or a 500 if a server error is encountered.
\end{indented}

\noindent\textbf{DELETE \texttt{/tour/:name}}

\begin{indented}{1cm}
	Deletes all versions of the tour with the given name from the server.
	Returns 200 if successful, along with a message saying how many versions
	were deleted, 404 if no tour with that name could be found, or 500 if a
	server error was encountered.
\end{indented}

\section{}

Appendix two text goes here.
